### 2017-09-23 monograph/thesis/chapters/implementation.tex
Fixed \cleardoublepage usaged across the project files.

% The \phantomsection command is needed to create a link to a place in the document that is not a
% figure, equation, table, section, subsection, chapter, etc.
%
% When do I need to invoke \phantomsection?
% https://tex.stackexchange.com/questions/44088/when-do-i-need-to-invoke-phantomsection
\cleardoublepage
\phantomsection

@@

    O objeto neste trabalho de TCC proposto aqui não é inicialmente suportar todas as regras de
    formatação de todas as linguagens de programação, mas a criação de uma estrutura básica inicial
    e robusta que sejam capaz de ser desenvolvida a ponto de ser facilmente expandida, tanto na
    adição de novos módulos de processamento no programa escrito, tanto pelo usuário final na
    escrita dos arquivos de programação.

    A teoria da técnica empregada é muito simples, mas diferente das atuais por que é atribuído ao
    usuário final a responsabilidade de dizer onde será realizado o beautifying do modulo que está
    se configurando. Esse é o preço a pagar para permitir a criação de um Beautifier Universal.
    Quando diz-se fácil configuração, refire-se a não necessidade de recorrer a programação ´C++',
    i.e., alterar o código fonte do programa para permitir/especificar onde devem ser realizadas as
    alterações de beautifying.

\subsubsection{Objetivos Gerais}

@@

        Escrever o programa em C++ ou afins, para permitir também que a formação/beautifying seja
        (em trabalhos futuros/talvez nesse) dinâmico, isto é, na medida que você digita o texto, ele
        é formatado para você. Assim você pode focar mais em escrever o código, ao invés que se
        preocupar com o espaçamento, alinhamento, parenteses, linhas novas, e o que mais que seja.

>>>>

% The \phantomsection command is needed to create a link to a place in the document that is not a
% figure, equation, table, section, subsection, chapter, etc.
%
% When do I need to invoke \phantomsection?
% https://tex.stackexchange.com/questions/44088/when-do-i-need-to-invoke-phantomsection
\phantomsection

@@

    The object in the proposed thesis is not initially to support all the
    formatting rules for all programming languages, but the creation of an
    initial and robust basic formatter capable of being developed to the point
    of being easily expanded by programmers with new processing modules and by
    end users writing the formatting configuration files.

    The theory of the technique proposed is quite simple, but different from the
    usual approach because the end user is assigned the responsibility to
    dictate more precisely how the beautifying being configured will be
    performed. Such tradeoff is the price to pay to allow the creation of a
    Universal Beautifier. But notice when it is said, it is supposed to be easy
    to set up, it is meant to not be required to do `C++' programming, i.e.
    change the source code of the program to set/specify where the beautifying
    changes are supposed to be performed.

\subsubsection{General Goals}

@@

        \item Write the program in C++ for greater performance, allowing the
        formating/beautifying to be dynamic, i.e., as you type the text, the
        text is formatted for you. So you can focus more on writing the code,
        rather than worrying about spacing, alignment, parentheses, new lines,
        and whatever else.
